Online {\IterComp}

### 2017-09-13 cgo18mscr.tex
minor change

\noindent\textbf{Populating the edge flows:}
Intuitively, if all the edge flows are known for the complement of a spanning tree
then at any leaf of the spanning tree there is only one unknown edge flow.
This unknown edge flow can be calculated by Kirchhoff's first law.
This process repeats as a bottom-up propagation until all the unknown edge flows
have been calculated.
This algorithm can be formally defined as a post-order traversal on the spanning
tree.
Let $G$ be the CFG.
This algorithm first initializes the edge flows $D_{(u,v)}$, for each edge
$(u,v)$ in the CFG, as follows:
\[
D_{(u,v)} \gets
\begin{cases}
    P_{(u,v)} & \quad \text{if edge $(u,v)$ has a probe $P_{(u,v)}$}\\
    0       & \quad \text{otherwise}
\end{cases}
\]
Afterwards, for each vertex $u\in G$, in a post-order traversal of the spanning tree,
we can use the Kirchhoff's first law and apply the following operations
in a symbolic fashion:
\[
\Sigma^+_u = \sum_{v\in N^+(u)} D_{(u,v)}
\]
\[
\Sigma^-_u = \sum_{v\in N^-(u)} D_{(v,u)}
\]
\[
\forall v\in N^+(u):  D_{(u,v)} \gets
\begin{cases}
    D_{(u,v)} & \quad \text{if $D_{(u,v)}\neq 0$}\\
    \Sigma^-_u - \Sigma^+_u       & \quad \text{otherwise}
\end{cases}
\]
\[
\forall v\in N^-(u):  D_{(v,u)} \gets
\begin{cases}
    D_{(v,u)} & \quad \text{if $D_{(v,u)}\neq 0$}\\
    \Sigma^+_u - \Sigma^-_u       & \quad \text{otherwise}
\end{cases}
\]

\noindent\textbf{Composing the aggregated value of the probes:}
If $x$ is a symbolic expression, then $\kappa_P(x)$ represents the coefficient
of the term $P$ in $x$.
In our case, $\kappa_P(x)$ will belong to the set $\{-1,0,1\}$.
Then, for all probes $P$:
\[
\omega(P) = \sum_{u\in G} \kappa_P(\Sigma^+_u)w(u)
\]

>>>>

\paragraph{Populating the edge flows:}
Intuitively, if all the edge flows are known for the complement of a spanning tree
then at any leaf of the spanning tree there is only one unknown edge flow.
This unknown edge flow can be calculated by Kirchhoff's first law.
This process repeats as a bottom-up propagation until all the unknown edge flows
have been calculated.
This algorithm can be formally defined as a post-order traversal on the spanning
tree.
Let $G$ be the CFG.
This algorithm first initializes the edge flows $D_{(u,v)}$, for each edge
$(u,v)$ in the CFG, as follows:
\[
D_{(u,v)} \gets
\begin{cases}
    P_{(u,v)} & \quad \text{if edge $(u,v)$ has a probe $P_{(u,v)}$}\\
    0       & \quad \text{otherwise}
\end{cases}
\]
Afterwards, for each vertex $u\in G$, in a post-order traversal of the spanning tree,
we can use the Kirchhoff's first law and apply the following operations
in a symbolic fashion:
\[
\Sigma^+_u = \sum_{v\in N^+(u)} D_{(u,v)}
\]
\[
\Sigma^-_u = \sum_{v\in N^-(u)} D_{(v,u)}
\]
\[
\forall v\in N^+(u):  D_{(u,v)} \gets
\begin{cases}
    D_{(u,v)} & \quad \text{if $D_{(u,v)}\neq 0$}\\
    \Sigma^-_u - \Sigma^+_u       & \quad \text{otherwise}
\end{cases}
\]
\[
\forall v\in N^-(u):  D_{(v,u)} \gets
\begin{cases}
    D_{(v,u)} & \quad \text{if $D_{(v,u)}\neq 0$}\\
    \Sigma^+_u - \Sigma^-_u       & \quad \text{otherwise}
\end{cases}
\]

\paragraph{Composing the aggregated value of the probes:}
If $x$ is a symbolic expression, then $\kappa_P(x)$ represents the coefficient
of the term $P$ in $x$.
In our case, $\kappa_P(x)$ will belong to the set $\{-1,0,1\}$.
Then, for all probes $P$:
\[
\omega(P) = \sum_{u\in G} \kappa_P(\Sigma^+_u)w(u)
\]
